Make a README

### 2025-01-27 make_readme.qmd
Track all (recursive) deps

# Then, identify the system dependencies
# of your direct dependencies.
renv::dependencies()$Package |>
  unique() |>
  pak::pkg_sysreqs()
```

>>>>

# Find all dependencies
deps <- renv::dependencies()$Package |>
   unique() |>
   pak::pkg_deps(dependencies = NA) |>
   getElement("package")

# Identify the system dependencies
pak::pkg_sysreqs(deps)
```
